---
title: "Degree Heating Month Analysis"
author: "Vanessa"
date: "`r lubridate::today()`"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Loading_Packages, message = FALSE, include = FALSE}
library(tidyverse)
library(lubridate)
library(dplyr)
library(patchwork)
library(colorspace)
library(rmarkdown)
library(tsibble)
library(scales)
library(kableExtra)
```

```{r CCI_Data_with_mmm_from_sst, include = FALSE}

CCI_BRS05 <- read_csv(here::here("data_raw", "CCI_BRS05_with_mmm_and_dhw.csv"))
CCI_BRS07 <- read_csv(here::here("data_raw", "CCI_BRS07_with_mmm_and_dhw.csv"))
CCI_BUN05A <- read_csv(here::here("data_raw", "CCI_BUN05A_with_mmm_and_dhw.csv"))
CCI_Bundegi <- read_csv(here::here("data_raw", "CCI_Bundegi_with_mmm_and_dhw.csv"))
CCI_DAR3 <- read_csv(here::here("data_raw", "CCI_DAR3_with_mmm_and_dhw.csv"))
CCI_DARL <- read_csv(here::here("data_raw", "CCI_DARL_with_mmm_and_dhw.csv"))
CCI_HAB05B <- read_csv(here::here("data_raw", "CCI_HAB05B_with_mmm_and_dhw.csv"))
CCI_HAB10A <- read_csv(here::here("data_raw", "CCI_HAB10A_with_mmm_and_dhw.csv"))
CCI_SCOTT_RPO_1 <- read_csv(here::here("data_raw", "CCI_SCOTT_RPO_1_with_mmm_and_dhw.csv"))
CCI_SCOTT_SL4 <- read_csv(here::here("data_raw", "CCI_SCOTT_SL4_with_mmm_and_dhw.csv"))
CCI_SCOTT_SS3 <- read_csv(here::here("data_raw", "CCI_SCOTT_SS3_with_mmm_and_dhw.csv"))
CCI_SCOTTNR1 <- read_csv(here::here("data_raw", "CCI_SCOTTNR1_with_mmm_and_dhw.csv"))
CCI_SCOTTSL1 <- read_csv(here::here("data_raw", "CCI_SCOTTSL1_with_mmm_and_dhw.csv"))
CCI_SCOTTSL2 <- read_csv(here::here("data_raw", "CCI_SCOTTSL2_with_mmm_and_dhw.csv"))
CCI_SCOTTSL3 <- read_csv(here::here("data_raw", "CCI_SCOTTSL3_with_mmm_and_dhw.csv"))
CCI_SCOTTSS1 <- read_csv(here::here("data_raw", "CCI_SCOTTSS1_with_mmm_and_dhw.csv"))
CCI_SCOTTSS2 <- read_csv(here::here("data_raw", "CCI_SCOTTSS2_with_mmm_and_dhw.csv"))
CCI_Tantabiddi <- read_csv(here::here("data_raw", "CCI_Tantabiddi_with_mmm_and_dhw.csv"))
CCI_TNT <- read_csv(here::here("data_raw", "CCI_TNT_with_mmm_and_dhw.csv"))
CCI_TNT07C <- read_csv(here::here("data_raw", "CCI_TNT07C_with_mmm_and_dhw.csv"))
CCI_Wallabi_Island <- read_csv(here::here("data_raw", "CCI_Wallabi_Island_with_mmm_and_dhw.csv"))

```

```{r NOAA_Data_with_mmm_from_sst, include = FALSE}

NOAA_BRS05 <- read_csv(here::here("data_raw", "NOAA_BRS05_with_mmm_and_dhw.csv"))
NOAA_BRS07 <- read_csv(here::here("data_raw", "NOAA_BRS07_with_mmm_and_dhw.csv"))
NOAA_BUN05A <- read_csv(here::here("data_raw", "NOAA_BUN05A_with_mmm_and_dhw.csv"))
NOAA_Bundegi <- read_csv(here::here("data_raw", "NOAA_Bundegi_with_mmm_and_dhw.csv"))
NOAA_DAR3 <- read_csv(here::here("data_raw", "NOAA_DAR3_with_mmm_and_dhw.csv"))
NOAA_DARL <- read_csv(here::here("data_raw", "NOAA_DAR_Long_with_mmm_and_dhw.csv"))
NOAA_HAB05B <- read_csv(here::here("data_raw", "NOAA_SST_HAB05B_SrCa_with_mmm_and_dhw.csv"))
NOAA_HAB10A <- read_csv(here::here("data_raw", "NOAA_SST_HAB10A_SrCa_with_mmm_and_dhw.csv"))
NOAA_SCOTT_RPO_1 <- read_csv(here::here("data_raw", "NOAA_SCOTT_RPO_1_with_mmm_and_dhw.csv"))
NOAA_SCOTT_SL4 <- read_csv(here::here("data_raw", "NOAA_SCOTT_SL4_with_mmm_and_dhw.csv"))
NOAA_SCOTT_SS3 <- read_csv(here::here("data_raw", "NOAA_SCOTT_SS3_with_mmm_and_dhw.csv"))
NOAA_SCOTTNR1 <- read_csv(here::here("data_raw", "NOAA_SCOTTNR1_with_mmm_and_dhw.csv"))
NOAA_SCOTTSL1 <- read_csv(here::here("data_raw", "NOAA_SCOTTSL1_with_mmm_and_dhw.csv"))
NOAA_SCOTTSL2 <- read_csv(here::here("data_raw", "NOAA_SCOTTSL2_with_mmm_and_dhw.csv"))
NOAA_SCOTTSL3 <- read_csv(here::here("data_raw", "NOAA_SCOTTSL3_with_mmm_and_dhw.csv"))
NOAA_SCOTTSS1 <- read_csv(here::here("data_raw", "NOAA_SCOTTSS1_with_mmm_and_dhw.csv"))
NOAA_SCOTTSS2 <- read_csv(here::here("data_raw", "NOAA_SCOTTSS2_with_mmm_and_dhw.csv"))
NOAA_Tantabiddi <- read_csv(here::here("data_raw", "NOAA_Tantabiddi_with_mmm_and_dhw.csv"))
NOAA_TNT <- read_csv(here::here("data_raw", "NOAA_TNT_with_mmm_and_dhw.csv"))
NOAA_TNT07C <- read_csv(here::here("data_raw", "NOAA_TNT07C_with_mmm_and_dhw.csv"))
NOAA_Wallabi_Island <- read_csv(here::here("data_raw", "NOAA_Wallabi_Island_with_mmm_and_dhw.csv"))
```

```{r CCore_Data_with_mmm_from_sst, include = FALSE}
#CCI Data
CCore_BRS05_CCI <- read_csv(here::here("data_raw", "CCore_SST_BRS05_CCI_with_mmm.csv")) %>%
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_BRS07_CCI <- read_csv(here::here("data_raw", "CCore_SST_BRS07_CCI_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_DARL_CCI <- read_csv(here::here("data_raw", "CCore_SST_DARL_CCI_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_Wallabi_Island_CCI <- read_csv(here::here("data_raw", "CCore_SST_Wallabi_Island_CCI_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))

#CCI Data - read TNT data for importing MMM_from_SST column to 13TNT and 08TNT
CCore_TNT_CCI <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_TNT_CCI_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_13TNT_CCI <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_13TNT_CCI.csv")) %>% 
  rename(Date = date) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(Latitude = "-21.91", Longitude = "113.97", mmm_from_sst = "27.92379", yearmonth = yearmonth(Date))
CCore_08TNT_CCI <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_08TNT_CCI.csv")) %>% 
  rename(Date = date) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(Latitude = "-21.91", Longitude = "113.97", mmm_from_sst = "27.92379", yearmonth = yearmonth(Date))

#NOAA Data
CCore_BRS05_NOAA <- read_csv(here::here("data_raw", "CCore_SST_BRS05_NOAA_with_mmm.csv")) %>%
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_BRS07_NOAA <- read_csv(here::here("data_raw", "CCore_SST_BRS07_NOAA_with_mmm.csv")) %>%
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_DARL_NOAA <- read_csv(here::here("data_raw", "CCore_SST_DARL_NOAA_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_Wallabi_Island_NOAA <- read_csv(here::here("data_raw", "CCore_SST_Wallabi_Island_NOAA_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))

#NOAA Data - read TNT data for importing MMM_from_SST column to 13TNT and 08TNT
CCore_TNT_NOAA <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_TNT_NOAA_with_mmm.csv")) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(yearmonth = yearmonth(Date))
CCore_13TNT_NOAA <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_13TNT_NOAA.csv")) %>%
  rename(Date = date) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(Latitude = "-21.91", Longitude = "113.97", mmm_from_sst = "28.43935", yearmonth = yearmonth(Date))
CCore_08TNT_NOAA <- read_csv(here::here("data_raw", "CCore_SST_Ningaloo_08TNT_NOAA.csv")) %>%
  rename(Date = date) %>% 
  mutate(Date = round_date(Date, unit = "month")) %>% 
  mutate(Latitude = "-21.91", Longitude = "113.97", mmm_from_sst = "28.43935", yearmonth = yearmonth(Date))

```

#Date Range of Coral Cores
```{r start_and_end_date_CCore, echo = FALSE, message = FALSE}
Date_BRS05_CCI <- CCore_BRS05_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()
Date_BRS05_NOAA <- CCore_BRS05_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()

Date_BRS07_CCI <- CCore_BRS07_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()
Date_BRS07_NOAA <- CCore_BRS07_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()

Date_DARL_CCI <- CCore_DARL_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()
Date_DARL_NOAA <- CCore_DARL_NOAA %>% 
 mutate(start_date = year(min(Date)), end_date = year(end_date)) %>% 
  select(Site, start_date, end_date) %>% 
  distinct()

Date_TNT_CCI <- CCore_TNT_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>%
  select(Site, start_date, end_date) %>% 
  distinct()
Date_TNT_NOAA <- CCore_TNT_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>%
  select(Site, start_date, end_date) %>% 
  distinct()

Date_13TNT_CCI <- CCore_13TNT_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(max(Date)), Site = "13TNT") %>% 
  select(Site, start_date, end_date,) %>% 
  distinct()
Date_13TNT_NOAA <- CCore_13TNT_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(max(Date)), Site = "13TNT") %>% 
  select(Site, start_date, end_date) %>% 
  distinct()

Date_08TNT_CCI <- CCore_08TNT_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(max(Date)), Site = "08TNT") %>% 
  select(Site, start_date, end_date) %>% 
  distinct()
Date_08TNT_NOAA <- CCore_08TNT_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(max(Date)), Site = "08TNT") %>% 
  select(Site, start_date, end_date) %>% 
  distinct()

Date_Wallabi_Island_CCI <- CCore_Wallabi_Island_CCI %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>%
  select(Site, start_date, end_date) %>% 
  distinct()
Date_Wallabi_Island_NOAA <- CCore_Wallabi_Island_NOAA %>% 
  mutate(start_date = year(min(Date)), end_date = year(end_date)) %>%
  select(Site, start_date, end_date) %>% 
  distinct()

Date_Coral_Core <- rbind(Date_BRS05_CCI, Date_BRS05_NOAA, Date_BRS07_CCI, Date_BRS07_NOAA, Date_DARL_CCI, Date_DARL_NOAA, Date_TNT_CCI, Date_TNT_NOAA, Date_13TNT_CCI, Date_13TNT_NOAA, Date_08TNT_CCI, Date_08TNT_NOAA, Date_Wallabi_Island_CCI, Date_Wallabi_Island_NOAA)

kbl(Date_Coral_Core, col.names = c("Site", "Start Year", "End Year")) %>% 
  kable_styling(position = "center")
  

```


```{r scan_gaps, include = FALSE}
#scan_gaps(CCI_Wallabi_Island)
#scan_gaps(NOAA_Wallabi_Island)

#checked - no gaps in CCI and NOAA datasets 
#using as_tsibble(data, index = date) and scan_gaps

#read Coral Core calibrated by CCI  as tsibbles and scan gaps in Coral Cores
ts_BRS05_CCI_Core <- as_tsibble(CCore_BRS05_CCI, index = yearmonth)
scan_gaps(ts_BRS05_CCI_Core) #47 gaps

ts_BRS07_CCI_Core <- as_tsibble(CCore_BRS07_CCI, index = yearmonth)
scan_gaps(ts_BRS07_CCI_Core) #47 gaps

ts_DARL_CCI_Core <- as_tsibble(CCore_DARL_CCI, index = yearmonth)
scan_gaps(ts_DARL_CCI_Core) #41 gaps

ts_TNT_CCI_Core <- as_tsibble(CCore_TNT_CCI, index = yearmonth)
scan_gaps(ts_TNT_CCI_Core) #15 gaps

ts_13TNT_CCI_Core <- CCore_13TNT_CCI %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>% 
  distinct() %>% 
  as_tsibble(., index = yearmonth)
scan_gaps(ts_13TNT_CCI_Core)  #23 gaps

ts_08TNT_CCI_Core <- CCore_08TNT_CCI %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>% 
  distinct() %>% 
  as_tsibble(., index = yearmonth)
scan_gaps(ts_08TNT_CCI_Core) #24 gaps

ts_Wallabi_Island_CCI_Core <- as_tsibble(CCore_Wallabi_Island_CCI, index = yearmonth)
scan_gaps(ts_Wallabi_Island_CCI_Core) #15 gaps

#read Coral Core calibrated by NOAA  as tsibbles and scan gaps in Coral Cores

ts_BRS05_NOAA_Core <- as_tsibble(CCore_BRS05_NOAA, index = yearmonth)
scan_gaps(ts_BRS05_NOAA_Core) #47 gaps

ts_BRS07_NOAA_Core <- as_tsibble(CCore_BRS07_NOAA, index = yearmonth)
scan_gaps(ts_BRS07_NOAA_Core) #47 gaps

ts_DARL_NOAA_Core <- as_tsibble(CCore_DARL_NOAA, index = yearmonth)
scan_gaps(ts_DARL_NOAA_Core) #41 gaps

ts_TNT_NOAA_Core <- as_tsibble(CCore_TNT_NOAA, index = yearmonth)
scan_gaps(ts_TNT_NOAA_Core) #15 gaps

ts_13TNT_NOAA_Core <- CCore_13TNT_NOAA %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>% 
  distinct() %>% 
  as_tsibble(., index = yearmonth)
scan_gaps(ts_13TNT_NOAA_Core) #23 gaps

ts_08TNT_NOAA_Core <- CCore_08TNT_NOAA %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup %>%
  distinct() %>% 
  as_tsibble(., index = yearmonth)
scan_gaps(ts_08TNT_NOAA_Core) #24 gaps

ts_Wallabi_Island_NOAA_Core <- as_tsibble(CCore_Wallabi_Island_NOAA, index = yearmonth)
scan_gaps(ts_Wallabi_Island_NOAA_Core) #15 gaps

```

# Degree Heating Month Anomaly Time Series Plots:      



```{r SST_Anomaly_TS, echo = FALSE}
#sst was averaged monthly and new column with sst_monthly generated
#duplicate rows are removed with distinct()
#date column into date format
#anomaly column is generated for ts plots

#BRS05

CCI_BRS05 <- CCI_BRS05 %>% 
  mutate(Reef_Site = "BRS05", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)
  

NOAA_BRS05 <- NOAA_BRS05 %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


CCore_BRS05_CCI <- CCore_BRS05_CCI %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (CCI)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_BRS05_NOAA <- CCore_BRS05_NOAA %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (NOAA)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

BRS05_Combined <- rbind(CCI_BRS05, NOAA_BRS05, CCore_BRS05_CCI, CCore_BRS05_NOAA)

ggplot(BRS05_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of BRS05 (-14.11, 123.54) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#BRS07
CCI_BRS07 <- CCI_BRS07 %>% 
  mutate(Reef_Site = "BRS07", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


NOAA_BRS07 <- NOAA_BRS07 %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

CCore_BRS07_CCI <- CCore_BRS07_CCI %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (CCI)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_BRS07_NOAA <- CCore_BRS07_NOAA %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (NOAA)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)


BRS07_Combined <- rbind(CCI_BRS07, NOAA_BRS07, CCore_BRS07_CCI, CCore_BRS07_NOAA)

ggplot(BRS07_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of BRS07 (-14.12, 123.55) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#DAR3
CCI_DAR3 <- CCI_DAR3 %>% 
  mutate(Reef_Site = "DAR3", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_DAR3 <- NOAA_DAR3 %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


DAR3_Combined <- rbind(CCI_DAR3, NOAA_DAR3)

ggplot(DAR3_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of DAR3 (-12.10, 96.88) Monthly SST anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#DAR Long
CCI_DARL <- CCI_DARL %>% 
  mutate(Reef_Site = "DAR Long", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_DARL <- NOAA_DARL %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


CCore_DARL_CCI <- CCore_DARL_CCI %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (CCI)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_DARL_NOAA <- CCore_DARL_NOAA %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (NOAA)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

DARL_Combined <- rbind(CCI_DARL, NOAA_DARL, CCore_DARL_CCI, CCore_DARL_NOAA)

ggplot(DARL_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of DAR Long (-12.09, 96.88) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Scott_RPO_1
CCI_SCOTT_RPO_1 <- CCI_SCOTT_RPO_1 %>% 
  mutate(Reef_Site = "SCOTT_RPO_1", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTT_RPO_1 <- NOAA_SCOTT_RPO_1 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTT_RPO_1_Combined <- rbind(CCI_SCOTT_RPO_1, NOAA_SCOTT_RPO_1)

ggplot(SCOTT_RPO_1_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTT_RPO_1 (-14.06, 121.78) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Scott_SL4
CCI_SCOTT_SL4 <- CCI_SCOTT_SL4 %>% 
  mutate(Reef_Site = "SCOTT_SL4", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTT_SL4 <- NOAA_SCOTT_SL4 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTT_SL4_Combined <- rbind(CCI_SCOTT_SL4, NOAA_SCOTT_SL4)

ggplot(SCOTT_SL4_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTT_SL4 (-14.02, 121.86) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )
  

#Scott_SS3
CCI_SCOTT_SS3 <- CCI_SCOTT_SS3 %>% 
  mutate(Reef_Site = "SCOTT_SS3", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTT_SS3 <- NOAA_SCOTT_SS3 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTT_SS3_Combined <- rbind(CCI_SCOTT_SS3, NOAA_SCOTT_SS3)

ggplot(SCOTT_SS3_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTT_SS3 (-13.64, 122.03) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottNR1
CCI_SCOTTNR1 <- CCI_SCOTTNR1 %>% 
  mutate(Reef_Site = "SCOTTNR1", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTNR1 <- NOAA_SCOTTNR1 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTNR1_Combined <- rbind(CCI_SCOTTNR1, NOAA_SCOTTNR1)

ggplot(SCOTTNR1_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTNR1 (-13.99, 121.88) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottSL1
CCI_SCOTTSL1 <- CCI_SCOTTSL1 %>% 
  mutate(Reef_Site = "SCOTTSL1", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTSL1 <- NOAA_SCOTTSL1 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTSL1_Combined <- rbind(CCI_SCOTTSL1, NOAA_SCOTTSL1)

ggplot(SCOTTSL1_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTSL1 (-14.08, 121.95) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottSL2
CCI_SCOTTSL2 <- CCI_SCOTTSL2 %>% 
  mutate(Reef_Site = "SCOTTSL2", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTSL2 <- NOAA_SCOTTSL2 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTSL2_Combined <- rbind(CCI_SCOTTSL2, NOAA_SCOTTSL2)

ggplot(SCOTTSL2_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTSL2 (-14.19, 121.80) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottSL3
CCI_SCOTTSL3 <- CCI_SCOTTSL3 %>% 
  mutate(Reef_Site = "SCOTTSL3", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTSL3 <- NOAA_SCOTTSL3 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTSL3_Combined <- rbind(CCI_SCOTTSL3, NOAA_SCOTTSL3)

ggplot(SCOTTSL3_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTSL3 (-14.07, 121.78) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottSS1
CCI_SCOTTSS1 <- CCI_SCOTTSS1 %>% 
  mutate(Reef_Site = "SCOTTSS1", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTSS1 <- NOAA_SCOTTSS1 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTSS1_Combined <- rbind(CCI_SCOTTSS1, NOAA_SCOTTSS1)

ggplot(SCOTTSS1_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTSS1 (-14.08, 121.98) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#ScottSS2
CCI_SCOTTSS2 <- CCI_SCOTTSS2 %>% 
  mutate(Reef_Site = "SCOTTSS2", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_SCOTTSS2 <- NOAA_SCOTTSS2 %>% 
  mutate(Data_Type = "NOAA", Reef_Site = subsite, Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

SCOTTSS2_Combined <- rbind(CCI_SCOTTSS2, NOAA_SCOTTSS2)

ggplot(SCOTTSS2_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of SCOTTSS2 (-13.92, 121.92) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Ningaloo BUN05A
CCI_BUN05A <- CCI_BUN05A %>% 
  mutate(Reef_Site = "BUN05A", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_BUN05A <- NOAA_BUN05A %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

BUN05A_Combined <- rbind(CCI_BUN05A, NOAA_BUN05A)

ggplot(BUN05A_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of BUN05A (-21.84, 114.18) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Ningaloo Bundegi
CCI_Bundegi <- CCI_Bundegi %>% 
  mutate(Reef_Site = "Bundegi", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_Bundegi <- NOAA_Bundegi %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

Bundegi_Combined <- rbind(CCI_Bundegi, NOAA_Bundegi)

ggplot(Bundegi_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of 08BND and 13BND (-21.87, 114.16) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Ningaloo Tantabiddi 13TNT
CCI_Tantabiddi_13TNT <- CCI_Tantabiddi %>% 
  mutate(Reef_Site = "13TNT", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_Tantabiddi_13TNT <- NOAA_Tantabiddi %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  mutate(Reef_Site = "13TNT") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


CCore_13TNT_CCI <- CCore_13TNT_CCI %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst_monthly = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>%  
  select(-sst) %>%
  distinct() %>% 
  rename(date = yearmonth) %>% 
  mutate(Reef_Site = "13TNT", Data_Type = "Coral Core (CCI)", anomaly = ( as.numeric(sst_monthly) - as.numeric(mmm_from_sst)), monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_13TNT_NOAA <- CCore_13TNT_NOAA %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst_monthly = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>%  
  select(-sst) %>%
  distinct() %>% 
  rename(date = yearmonth) %>% 
  mutate(Reef_Site = "13TNT", Data_Type = "Coral Core (NOAA)", anomaly = ( as.numeric(sst_monthly) - as.numeric(mmm_from_sst)), monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

Tantabiddi_13TNT_Combined <- rbind(CCI_Tantabiddi_13TNT, NOAA_Tantabiddi_13TNT, CCore_13TNT_CCI, CCore_13TNT_NOAA)

ggplot(Tantabiddi_13TNT_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of 13TNT (-21.91, 113.97) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )

#Ningaloo Tantabiddi 08TNT
CCI_Tantabiddi_08TNT <- CCI_Tantabiddi %>% 
  mutate(Reef_Site = "08TNT", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_Tantabiddi_08TNT <- NOAA_Tantabiddi %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  mutate(Reef_Site = "08TNT") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)


CCore_08TNT_CCI <- CCore_08TNT_CCI %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst_monthly = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>% 
  select(-sst) %>% 
  distinct() %>%  
  rename(date = yearmonth) %>% 
  mutate(Reef_Site = "08TNT", Data_Type = "Coral Core (CCI)", anomaly = ( as.numeric(sst_monthly) - as.numeric(mmm_from_sst)), monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_08TNT_NOAA <- CCore_08TNT_NOAA %>% 
  select(-Date) %>% 
  group_by(yearmonth) %>% 
  mutate(sst_monthly = mean(sst), SrCa = mean(SrCa)) %>% 
  ungroup() %>%  
  select(-sst) %>%
  distinct() %>% 
  rename(date = yearmonth) %>% 
  mutate(Reef_Site = "08TNT", Data_Type = "Coral Core (NOAA)", anomaly = ( as.numeric(sst_monthly) - as.numeric(mmm_from_sst)), monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

Tantabiddi_08TNT_Combined <- rbind(CCI_Tantabiddi_08TNT, NOAA_Tantabiddi_08TNT, CCore_08TNT_CCI, CCore_08TNT_NOAA)

ggplot(Tantabiddi_08TNT_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of 08TNT (-21.91, 113.97) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



#Ningaloo TNT
CCI_TNT <- CCI_TNT %>% 
  mutate(Reef_Site = "TNT", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_TNT <- NOAA_TNT %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

CCore_TNT_CCI <- CCore_TNT_CCI %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (CCI)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_TNT_NOAA <- CCore_TNT_NOAA %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (NOAA)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

TNT_Combined <- rbind(CCI_TNT, NOAA_TNT, CCore_TNT_CCI, CCore_TNT_NOAA)

ggplot(TNT_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of TNT (-21.9, 113.97) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Ningaloo TNT07C
CCI_TNT07C <- CCI_TNT07C %>% 
  mutate(Reef_Site = "TNT07C", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_TNT07C <- NOAA_TNT07C %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

TNT07C_Combined <- rbind(CCI_TNT07C, NOAA_TNT07C)

ggplot(TNT07C_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of TNT07C (-21.89, 113.96) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Houtman Abrolhos Wallabi Island
CCI_Wallabi_Island <- CCI_Wallabi_Island %>% 
  mutate(Reef_Site = "Wallabi Island", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_Wallabi_Island <- NOAA_Wallabi_Island %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

CCore_Wallabi_Island_CCI <- CCore_Wallabi_Island_CCI %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (CCI)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

CCore_Wallabi_Island_NOAA <- CCore_Wallabi_Island_NOAA %>% 
  rename(sst_monthly = sst, date = yearmonth, Reef_Site = Site) %>% 
  mutate(Data_Type = "Coral Core (NOAA)", anomaly = sst_monthly - mmm_from_sst, monthly_date = date) %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst, date, anomaly)

Wallabi_Island_Combined <- rbind(CCI_Wallabi_Island, NOAA_Wallabi_Island, CCore_Wallabi_Island_CCI, CCore_Wallabi_Island_NOAA)

ggplot(Wallabi_Island_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of Wallabi Island (-28.28, 113.46) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Houtman Abrolhos HAB05B
CCI_HAB05B <- CCI_HAB05B %>% 
  mutate(Reef_Site = "HAB05B", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_HAB05B <- NOAA_HAB05B %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

HAB05B_Combined <- rbind(CCI_HAB05B, NOAA_HAB05B)

ggplot(HAB05B_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of HAB05B (-28.46, 113.77) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


#Houtman Abrolhos HAB10A
CCI_HAB10A <- CCI_HAB10A %>% 
  mutate(Reef_Site = "HAB10A", Data_Type = "CCI") %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

NOAA_HAB10A <- NOAA_HAB10A %>% 
  mutate(Data_Type = "NOAA", Year = year(Date), Month = month((Date), label = TRUE)) %>% 
  mutate(monthly_date = str_c(Year, Month, sep = "-")) %>% 
  group_by(monthly_date) %>% 
  mutate(sst_monthly = mean(sst)) %>% 
  ungroup() %>% 
  select(sst_monthly, Latitude, Longitude, monthly_date, Reef_Site, Data_Type, mmm_from_sst) %>% 
  distinct() %>% 
  mutate(date = monthly_date, monthly_date = ym(monthly_date), anomaly = sst_monthly - mmm_from_sst)

HAB10A_Combined <- rbind(CCI_HAB10A, NOAA_HAB10A)

ggplot(HAB10A_Combined)+
  geom_line(aes(x = monthly_date, y = anomaly, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Time", y = "Monthly SST Anomaly", title = "Time Series of HAB10A (-28.46, 113.75) Monthly SST Anomalies") +
  scale_color_discrete_qualitative(name = "Data Source") +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


```
\newpage
```{r fill_gaps, include = FALSE}
# before calculating Degree Heating Months, it is important to fill gaps in time with 0
# prevent inaccurate running sum of DHM values when there is missing gap in time

CCore_BRS05_CCI <- CCore_BRS05_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "BRS05", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_BRS07_CCI <- CCore_BRS07_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "BRS07", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_DARL_CCI <- CCore_DARL_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "DARL", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_TNT_CCI <- CCore_TNT_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "TNT", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_13TNT_CCI <- CCore_13TNT_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "13TNT", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_08TNT_CCI <- CCore_08TNT_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "08TNT", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_Wallabi_Island_CCI <- CCore_Wallabi_Island_CCI %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "Wallabi Island", Data_Type = "Coral Core (CCI)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_BRS05_NOAA <- CCore_BRS05_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "BRS05", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_BRS07_NOAA <- CCore_BRS07_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "BRS07", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_DARL_NOAA <- CCore_DARL_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "DARL", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_TNT_NOAA <- CCore_TNT_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "TNT", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_13TNT_NOAA <- CCore_13TNT_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "13TNT", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_08TNT_NOAA <- CCore_08TNT_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "08TNT", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))

CCore_Wallabi_Island_NOAA <- CCore_Wallabi_Island_NOAA %>% 
  as_tsibble(index = date) %>% 
  fill_gaps(anomaly = 0, Reef_Site = "Wallabi Island", Data_Type = "Coral Core (NOAA)") %>% 
  as_tibble() %>% 
  mutate(monthly_date = as.Date(date))


```


\newpage

# **BRS05** Degree Heating Months Time Series


```{r DHM_BRS05, echo = FALSE, message = FALSE}

#DHM calculations for CCI dataset 
BRS05_DHM <- rep(0,nrow(CCI_BRS05))
BRS05_negative_anomaly <- 0
for (i in 1:nrow(CCI_BRS05)){
  if(CCI_BRS05$anomaly[i] > 0) {
    BRS05_negative_anomaly <- 
      BRS05_negative_anomaly + CCI_BRS05$anomaly[i]
  } else {
    BRS05_negative_anomaly <- 0
  }
  BRS05_DHM[i] <- BRS05_negative_anomaly
}

CCI_BRS05 <- CCI_BRS05 %>% 
  add_column(BRS05_DHM)

#DHM calculations for NOAA dataset
BRS05_DHM <- rep(0,nrow(NOAA_BRS05))
BRS05_negative_anomaly <- 0
for (i in 1:nrow(NOAA_BRS05)){
  if(NOAA_BRS05$anomaly[i] > 0) {
    BRS05_negative_anomaly <- 
      BRS05_negative_anomaly + NOAA_BRS05$anomaly[i]
  } else {
    BRS05_negative_anomaly <- 0
  }
  BRS05_DHM[i] <- BRS05_negative_anomaly
}

NOAA_BRS05 <- NOAA_BRS05 %>% 
  add_column(BRS05_DHM)

#DHM calculations for Coral Core (CCI) dataset
BRS05_DHM <- rep(0,nrow(CCore_BRS05_CCI))
BRS05_negative_anomaly <- 0
for (i in 1:nrow(CCore_BRS05_CCI)){
  if(CCore_BRS05_CCI$anomaly[i] > 0) {
    BRS05_negative_anomaly <- 
      BRS05_negative_anomaly + CCore_BRS05_CCI$anomaly[i]
  } else {
    BRS05_negative_anomaly <- 0
  }
  BRS05_DHM[i] <- BRS05_negative_anomaly
}

CCore_BRS05_CCI <- CCore_BRS05_CCI %>% 
  add_column(BRS05_DHM) %>% 
  mutate(date = as.Date(date))

#DHM calculations for Coral Core (NOAA) dataset
BRS05_DHM <- rep(0,nrow(CCore_BRS05_NOAA))
BRS05_negative_anomaly <- 0
for (i in 1:nrow(CCore_BRS05_NOAA)){
  if(CCore_BRS05_NOAA$anomaly[i] > 0) {
    BRS05_negative_anomaly <- 
      BRS05_negative_anomaly + CCore_BRS05_NOAA$anomaly[i]
  } else {
    BRS05_negative_anomaly <- 0
  }
  BRS05_DHM[i] <- BRS05_negative_anomaly
}

CCore_BRS05_NOAA <- CCore_BRS05_NOAA %>%
  add_column(BRS05_DHM) 

#Combining datasets with DHM calculations
BRS05_Combined <- rbind(CCI_BRS05, NOAA_BRS05, CCore_BRS05_CCI, CCore_BRS05_NOAA)

#DHM >= 1
High_BRS05_DHM <- BRS05_Combined %>% 
  filter(BRS05_DHM >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, BRS05_DHM) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = BRS05_DHM) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_BRS05_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in BRS05" = 6), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1985 to 2011")


#Visualising DHM values in CCI, NOAA and CCore 
BRS05_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = BRS05_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "BRS05 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


```

\newpage
# **BRS07** Degree Heating Months Time Series


```{r DHM_BRS07, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
BRS07_DHM <- rep(0,nrow(CCI_BRS07))
BRS07_negative_anomaly <- 0
for (i in 1:nrow(CCI_BRS07)){
  if(CCI_BRS07$anomaly[i] > 0) {
    BRS07_negative_anomaly <- 
      BRS07_negative_anomaly + CCI_BRS07$anomaly[i]
  } else {
    BRS07_negative_anomaly <- 0
  }
  BRS07_DHM[i] <- BRS07_negative_anomaly
}

CCI_BRS07 <- CCI_BRS07 %>% 
  add_column(BRS07_DHM)

#DHM calculations for NOAA dataset
BRS07_DHM <- rep(0,nrow(NOAA_BRS07))
BRS07_negative_anomaly <- 0
for (i in 1:nrow(NOAA_BRS07)){
  if(NOAA_BRS07$anomaly[i] > 0) {
    BRS07_negative_anomaly <- 
      BRS07_negative_anomaly + NOAA_BRS07$anomaly[i]
  } else {
    BRS07_negative_anomaly <- 0
  }
  BRS07_DHM[i] <- BRS07_negative_anomaly
}

NOAA_BRS07 <- NOAA_BRS07 %>% 
  add_column(BRS07_DHM)

#DHM calculations for Coral Core (CCI) dataset
BRS07_DHM <- rep(0,nrow(CCore_BRS07_CCI))
BRS07_negative_anomaly <- 0
for (i in 1:nrow(CCore_BRS07_CCI)){
  if(CCore_BRS07_CCI$anomaly[i] > 0) {
    BRS07_negative_anomaly <- 
      BRS07_negative_anomaly + CCore_BRS07_CCI$anomaly[i]
  } else {
    BRS07_negative_anomaly <- 0
  }
  BRS07_DHM[i] <- BRS07_negative_anomaly
}

CCore_BRS07_CCI <- CCore_BRS07_CCI %>% 
  add_column(BRS07_DHM)

#DHM calculations for Coral Core (NOAA) dataset
BRS07_DHM <- rep(0,nrow(CCore_BRS07_NOAA))
BRS07_negative_anomaly <- 0
for (i in 1:nrow(CCore_BRS07_NOAA)){
  if(CCore_BRS07_NOAA$anomaly[i] > 0) {
    BRS07_negative_anomaly <- 
      BRS07_negative_anomaly + CCore_BRS07_NOAA$anomaly[i]
  } else {
    BRS07_negative_anomaly <- 0
  }
  BRS07_DHM[i] <- BRS07_negative_anomaly
}

CCore_BRS07_NOAA <- CCore_BRS07_NOAA %>% 
  add_column(BRS07_DHM)

#Combining datasets with DHM calculations
BRS07_Combined <- rbind(CCI_BRS07, NOAA_BRS07, CCore_BRS07_CCI, CCore_BRS07_NOAA)

#DHM >= 1
High_BRS07_DHM <- BRS07_Combined %>% 
  filter(BRS07_DHM >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, BRS07_DHM) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = BRS07_DHM) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_BRS07_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in BRS07" = 5), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1985 to 2011")

#Visualising DHM values in CCI, NOAA and CCore 
BRS07_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = BRS07_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "BRS07 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )

```

\newpage
# **DAR3** Degree Heating Months Time Series

```{r DHM_DAR3, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
DAR3_DHM <- rep(0,nrow(CCI_DAR3))
DAR3_negative_anomaly <- 0
for (i in 1:nrow(CCI_DAR3)){
  if(CCI_DAR3$anomaly[i] > 0) {
    DAR3_negative_anomaly <- 
      DAR3_negative_anomaly + CCI_DAR3$anomaly[i]
  } else {
    DAR3_negative_anomaly <- 0
  }
  DAR3_DHM[i] <- DAR3_negative_anomaly
}

CCI_DAR3 <- CCI_DAR3 %>% 
  add_column(DAR3_DHM)

#DHM calculations for NOAA dataset
DAR3_DHM <- rep(0,nrow(NOAA_DAR3))
DAR3_negative_anomaly <- 0
for (i in 1:nrow(NOAA_DAR3)){
  if(NOAA_DAR3$anomaly[i] > 0) {
    DAR3_negative_anomaly <- 
      DAR3_negative_anomaly + NOAA_DAR3$anomaly[i]
  } else {
    DAR3_negative_anomaly <- 0
  }
  DAR3_DHM[i] <- DAR3_negative_anomaly
}

NOAA_DAR3 <- NOAA_DAR3 %>% 
  add_column(DAR3_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
DAR3_Combined <- rbind(CCI_DAR3, NOAA_DAR3)

#DHM in descending order
Max_DHM_CCI_DAR3 <- CCI_DAR3 %>% 
  arrange(desc(DAR3_DHM)) %>% 
  select(date, DAR3_DHM)
Max_DHM_NOAA_DAR3 <- NOAA_DAR3 %>% 
  arrange(desc(DAR3_DHM)) %>% 
  select(date, DAR3_DHM)


knitr::kable(list(Max_DHM_CCI_DAR3, Max_DHM_NOAA_DAR3), caption = "Degree Heating Month values in DAR3 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
DAR3_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = DAR3_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "DAR3 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```

\newpage
# **DAR Long** Degree Heating Months Time Series

```{r DHM_DARL, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
DARL_DHM <- rep(0,nrow(CCI_DARL))
DARL_negative_anomaly <- 0
for (i in 1:nrow(CCI_DARL)){
  if(CCI_DARL$anomaly[i] > 0) {
    DARL_negative_anomaly <- 
      DARL_negative_anomaly + CCI_DARL$anomaly[i]
  } else {
    DARL_negative_anomaly <- 0
  }
  DARL_DHM[i] <- DARL_negative_anomaly
}

CCI_DARL <- CCI_DARL %>% 
  add_column(DARL_DHM)

#DHM calculations for NOAA dataset
DARL_DHM <- rep(0,nrow(NOAA_DARL))
DARL_negative_anomaly <- 0
for (i in 1:nrow(NOAA_DARL)){
  if(NOAA_DARL$anomaly[i] > 0) {
    DARL_negative_anomaly <- 
      DARL_negative_anomaly + NOAA_DARL$anomaly[i]
  } else {
    DARL_negative_anomaly <- 0
  }
  DARL_DHM[i] <- DARL_negative_anomaly
}

NOAA_DARL <- NOAA_DARL %>% 
  add_column(DARL_DHM)

#DHM calculations for Coral Core (CCI) dataset
DARL_DHM <- rep(0,nrow(CCore_DARL_CCI))
DARL_negative_anomaly <- 0
for (i in 1:nrow(CCore_DARL_CCI)){
  if(CCore_DARL_CCI$anomaly[i] > 0) {
    DARL_negative_anomaly <- 
      DARL_negative_anomaly + CCore_DARL_CCI$anomaly[i]
  } else {
    DARL_negative_anomaly <- 0
  }
  DARL_DHM[i] <- DARL_negative_anomaly
}

CCore_DARL_CCI <- CCore_DARL_CCI %>% 
  add_column(DARL_DHM)

#DHM calculations for Coral Core (NOAA) dataset
DARL_DHM <- rep(0,nrow(CCore_DARL_NOAA))
DARL_negative_anomaly <- 0
for (i in 1:nrow(CCore_DARL_NOAA)){
  if(CCore_DARL_NOAA$anomaly[i] > 0) {
    DARL_negative_anomaly <- 
      DARL_negative_anomaly + CCore_DARL_NOAA$anomaly[i]
  } else {
    DARL_negative_anomaly <- 0
  }
  DARL_DHM[i] <- DARL_negative_anomaly
}

CCore_DARL_NOAA <- CCore_DARL_NOAA %>% 
  add_column(DARL_DHM)

#Combining datasets with DHM calculations
DARL_Combined <- rbind(CCI_DARL, NOAA_DARL, CCore_DARL_CCI, CCore_DARL_NOAA)

#DHM >= 1
High_DARL_DHM <- DARL_Combined %>% 
  filter(DARL_DHM >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, DARL_DHM) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = DARL_DHM) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_DARL_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in DAR Long" = 6), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1985 to 2009")

#Visualising DHM values in CCI, NOAA and CCore 
DARL_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = DARL_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "DARL Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```


\newpage
# **SCOTT_RPO_1** Degree Heating Months Time Series

```{r DHM_SCOTT_RPO_1, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTT_RPO_1_DHM <- rep(0,nrow(CCI_SCOTT_RPO_1))
SCOTT_RPO_1_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTT_RPO_1)){
  if(CCI_SCOTT_RPO_1$anomaly[i] > 0) {
    SCOTT_RPO_1_negative_anomaly <- 
      SCOTT_RPO_1_negative_anomaly + CCI_SCOTT_RPO_1$anomaly[i]
  } else {
    SCOTT_RPO_1_negative_anomaly <- 0
  }
  SCOTT_RPO_1_DHM[i] <- SCOTT_RPO_1_negative_anomaly
}

CCI_SCOTT_RPO_1 <- CCI_SCOTT_RPO_1 %>% 
  add_column(SCOTT_RPO_1_DHM)

#DHM calculations for NOAA dataset
SCOTT_RPO_1_DHM <- rep(0,nrow(NOAA_SCOTT_RPO_1))
SCOTT_RPO_1_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTT_RPO_1)){
  if(NOAA_SCOTT_RPO_1$anomaly[i] > 0) {
    SCOTT_RPO_1_negative_anomaly <- 
      SCOTT_RPO_1_negative_anomaly + NOAA_SCOTT_RPO_1$anomaly[i]
  } else {
    SCOTT_RPO_1_negative_anomaly <- 0
  }
  SCOTT_RPO_1_DHM[i] <- SCOTT_RPO_1_negative_anomaly
}

NOAA_SCOTT_RPO_1 <- NOAA_SCOTT_RPO_1 %>% 
  add_column(SCOTT_RPO_1_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTT_RPO_1_Combined <- rbind(CCI_SCOTT_RPO_1, NOAA_SCOTT_RPO_1)

#DHM in descending order
Max_DHM_CCI_SCOTT_RPO_1 <- CCI_SCOTT_RPO_1 %>% 
  arrange(desc(SCOTT_RPO_1_DHM)) %>% 
  select(date, SCOTT_RPO_1_DHM)
Max_DHM_NOAA_SCOTT_RPO_1 <- NOAA_SCOTT_RPO_1 %>% 
  arrange(desc(SCOTT_RPO_1_DHM)) %>% 
  select(date, SCOTT_RPO_1_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTT_RPO_1, Max_DHM_NOAA_SCOTT_RPO_1), caption = "Degree Heating Month values in SCOTT_RPO_1 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTT_RPO_1_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTT_RPO_1_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTT_RPO_1 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```

\newpage
# **SCOTT_SL4** Degree Heating Months Time Series

```{r DHM_SCOTT_SL4, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTT_SL4_DHM <- rep(0,nrow(CCI_SCOTT_SL4))
SCOTT_SL4_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTT_SL4)){
  if(CCI_SCOTT_SL4$anomaly[i] > 0) {
    SCOTT_SL4_negative_anomaly <- 
      SCOTT_SL4_negative_anomaly + CCI_SCOTT_SL4$anomaly[i]
  } else {
    SCOTT_SL4_negative_anomaly <- 0
  }
  SCOTT_SL4_DHM[i] <- SCOTT_SL4_negative_anomaly
}

CCI_SCOTT_SL4 <- CCI_SCOTT_SL4 %>% 
  add_column(SCOTT_SL4_DHM)

#DHM calculations for NOAA dataset
SCOTT_SL4_DHM <- rep(0,nrow(NOAA_SCOTT_SL4))
SCOTT_SL4_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTT_SL4)){
  if(NOAA_SCOTT_SL4$anomaly[i] > 0) {
    SCOTT_SL4_negative_anomaly <- 
      SCOTT_SL4_negative_anomaly + NOAA_SCOTT_SL4$anomaly[i]
  } else {
    SCOTT_SL4_negative_anomaly <- 0
  }
  SCOTT_SL4_DHM[i] <- SCOTT_SL4_negative_anomaly
}

NOAA_SCOTT_SL4 <- NOAA_SCOTT_SL4 %>% 
  add_column(SCOTT_SL4_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTT_SL4_Combined <- rbind(CCI_SCOTT_SL4, NOAA_SCOTT_SL4)

#DHM in descending order
Max_DHM_CCI_SCOTT_SL4 <- CCI_SCOTT_SL4 %>% 
  arrange(desc(SCOTT_SL4_DHM)) %>% 
  select(date, SCOTT_SL4_DHM)
Max_DHM_NOAA_SCOTT_SL4 <- NOAA_SCOTT_SL4 %>% 
  arrange(desc(SCOTT_SL4_DHM)) %>% 
  select(date, SCOTT_SL4_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTT_SL4, Max_DHM_NOAA_SCOTT_SL4), caption = "Degree Heating Month values in SCOTT_SL4 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTT_SL4_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTT_SL4_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTT_SL4 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```

\newpage
# **SCOTT_SS3** Degree Heating Months Time Series

```{r DHM_SCOTT_SS3, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTT_SS3_DHM <- rep(0,nrow(CCI_SCOTT_SS3))
SCOTT_SS3_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTT_SS3)){
  if(CCI_SCOTT_SS3$anomaly[i] > 0) {
    SCOTT_SS3_negative_anomaly <- 
      SCOTT_SS3_negative_anomaly + CCI_SCOTT_SS3$anomaly[i]
  } else {
    SCOTT_SS3_negative_anomaly <- 0
  }
  SCOTT_SS3_DHM[i] <- SCOTT_SS3_negative_anomaly
}

CCI_SCOTT_SS3 <- CCI_SCOTT_SS3 %>% 
  add_column(SCOTT_SS3_DHM)

#DHM calculations for NOAA dataset
SCOTT_SS3_DHM <- rep(0,nrow(NOAA_SCOTT_SS3))
SCOTT_SS3_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTT_SS3)){
  if(NOAA_SCOTT_SS3$anomaly[i] > 0) {
    SCOTT_SS3_negative_anomaly <- 
      SCOTT_SS3_negative_anomaly + NOAA_SCOTT_SS3$anomaly[i]
  } else {
    SCOTT_SS3_negative_anomaly <- 0
  }
  SCOTT_SS3_DHM[i] <- SCOTT_SS3_negative_anomaly
}

NOAA_SCOTT_SS3 <- NOAA_SCOTT_SS3 %>% 
  add_column(SCOTT_SS3_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTT_SS3_Combined <- rbind(CCI_SCOTT_SS3, NOAA_SCOTT_SS3)

#DHM in descending order
Max_DHM_CCI_SCOTT_SS3 <- CCI_SCOTT_SS3 %>% 
  arrange(desc(SCOTT_SS3_DHM)) %>% 
  select(date, SCOTT_SS3_DHM)
Max_DHM_NOAA_SCOTT_SS3 <- NOAA_SCOTT_SS3 %>% 
  arrange(desc(SCOTT_SS3_DHM)) %>% 
  select(date, SCOTT_SS3_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTT_SS3, Max_DHM_NOAA_SCOTT_SS3), caption = "Degree Heating Month values in SCOTT_SS3 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTT_SS3_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTT_SS3_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTT_SS3 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```


\newpage
# **SCOTTNR1** Degree Heating Months Time Series

```{r DHM_SCOTTNR1, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTTNR1_DHM <- rep(0,nrow(CCI_SCOTTNR1))
SCOTTNR1_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTNR1)){
  if(CCI_SCOTTNR1$anomaly[i] > 0) {
    SCOTTNR1_negative_anomaly <- 
      SCOTTNR1_negative_anomaly + CCI_SCOTTNR1$anomaly[i]
  } else {
    SCOTTNR1_negative_anomaly <- 0
  }
  SCOTTNR1_DHM[i] <- SCOTTNR1_negative_anomaly
}

CCI_SCOTTNR1 <- CCI_SCOTTNR1 %>% 
  add_column(SCOTTNR1_DHM)

#DHM calculations for NOAA dataset
SCOTTNR1_DHM <- rep(0,nrow(NOAA_SCOTTNR1))
SCOTTNR1_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTNR1)){
  if(NOAA_SCOTTNR1$anomaly[i] > 0) {
    SCOTTNR1_negative_anomaly <- 
      SCOTTNR1_negative_anomaly + NOAA_SCOTTNR1$anomaly[i]
  } else {
    SCOTTNR1_negative_anomaly <- 0
  }
  SCOTTNR1_DHM[i] <- SCOTTNR1_negative_anomaly
}

NOAA_SCOTTNR1 <- NOAA_SCOTTNR1 %>% 
  add_column(SCOTTNR1_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTNR1_Combined <- rbind(CCI_SCOTTNR1, NOAA_SCOTTNR1)

#DHM in descending order
Max_DHM_CCI_SCOTTNR1 <- CCI_SCOTTNR1 %>% 
  arrange(desc(SCOTTNR1_DHM)) %>% 
  select(date, SCOTTNR1_DHM)
Max_DHM_NOAA_SCOTTNR1 <- NOAA_SCOTTNR1 %>% 
  arrange(desc(SCOTTNR1_DHM)) %>% 
  select(date, SCOTTNR1_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTNR1, Max_DHM_NOAA_SCOTTNR1), caption = "Degree Heating Month values in SCOTTNR1 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTNR1_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTNR1_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTNR1 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```


\newpage
# **SCOTTSL1** Degree Heating Months Time Series

```{r DHM_SCOTTSL1, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTTSL1_DHM <- rep(0,nrow(CCI_SCOTTSL1))
SCOTTSL1_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTSL1)){
  if(CCI_SCOTTSL1$anomaly[i] > 0) {
    SCOTTSL1_negative_anomaly <- 
      SCOTTSL1_negative_anomaly + CCI_SCOTTSL1$anomaly[i]
  } else {
    SCOTTSL1_negative_anomaly <- 0
  }
  SCOTTSL1_DHM[i] <- SCOTTSL1_negative_anomaly
}

CCI_SCOTTSL1 <- CCI_SCOTTSL1 %>% 
  add_column(SCOTTSL1_DHM)

#DHM calculations for NOAA dataset
SCOTTSL1_DHM <- rep(0,nrow(NOAA_SCOTTSL1))
SCOTTSL1_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTSL1)){
  if(NOAA_SCOTTSL1$anomaly[i] > 0) {
    SCOTTSL1_negative_anomaly <- 
      SCOTTSL1_negative_anomaly + NOAA_SCOTTSL1$anomaly[i]
  } else {
    SCOTTSL1_negative_anomaly <- 0
  }
  SCOTTSL1_DHM[i] <- SCOTTSL1_negative_anomaly
}

NOAA_SCOTTSL1 <- NOAA_SCOTTSL1 %>% 
  add_column(SCOTTSL1_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTSL1_Combined <- rbind(CCI_SCOTTSL1, NOAA_SCOTTSL1)

#DHM in descending order
Max_DHM_CCI_SCOTTSL1 <- CCI_SCOTTSL1 %>% 
  arrange(desc(SCOTTSL1_DHM)) %>% 
  select(date, SCOTTSL1_DHM)
Max_DHM_NOAA_SCOTTSL1 <- NOAA_SCOTTSL1 %>% 
  arrange(desc(SCOTTSL1_DHM)) %>% 
  select(date, SCOTTSL1_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTSL1, Max_DHM_NOAA_SCOTTSL1), caption = "Degree Heating Month values in SCOTTSL1 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTSL1_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTSL1_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTSL1 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


 
```


\newpage
# **SCOTTSL2** Degree Heating Months Time Series

```{r DHM_SCOTTSL2, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTTSL2_DHM <- rep(0,nrow(CCI_SCOTTSL2))
SCOTTSL2_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTSL2)){
  if(CCI_SCOTTSL2$anomaly[i] > 0) {
    SCOTTSL2_negative_anomaly <- 
      SCOTTSL2_negative_anomaly + CCI_SCOTTSL2$anomaly[i]
  } else {
    SCOTTSL2_negative_anomaly <- 0
  }
  SCOTTSL2_DHM[i] <- SCOTTSL2_negative_anomaly
}

CCI_SCOTTSL2 <- CCI_SCOTTSL2 %>% 
  add_column(SCOTTSL2_DHM)

#DHM calculations for NOAA dataset
SCOTTSL2_DHM <- rep(0,nrow(NOAA_SCOTTSL2))
SCOTTSL2_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTSL2)){
  if(NOAA_SCOTTSL2$anomaly[i] > 0) {
    SCOTTSL2_negative_anomaly <- 
      SCOTTSL2_negative_anomaly + NOAA_SCOTTSL2$anomaly[i]
  } else {
    SCOTTSL2_negative_anomaly <- 0
  }
  SCOTTSL2_DHM[i] <- SCOTTSL2_negative_anomaly
}

NOAA_SCOTTSL2 <- NOAA_SCOTTSL2 %>% 
  add_column(SCOTTSL2_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTSL2_Combined <- rbind(CCI_SCOTTSL2, NOAA_SCOTTSL2)

#DHM in descending order
Max_DHM_CCI_SCOTTSL2 <- CCI_SCOTTSL2 %>% 
  arrange(desc(SCOTTSL2_DHM)) %>% 
  select(date, SCOTTSL2_DHM)
Max_DHM_NOAA_SCOTTSL2 <- NOAA_SCOTTSL2 %>% 
  arrange(desc(SCOTTSL2_DHM)) %>% 
  select(date, SCOTTSL2_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTSL2, Max_DHM_NOAA_SCOTTSL2), caption = "Degree Heating Month values in SCOTTSL2 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTSL2_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTSL2_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTSL2 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```

\newpage
# **SCOTTSL3** Degree Heating Months Time Series

```{r DHM_SCOTTSL3, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTTSL3_DHM <- rep(0,nrow(CCI_SCOTTSL3))
SCOTTSL3_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTSL3)){
  if(CCI_SCOTTSL3$anomaly[i] > 0) {
    SCOTTSL3_negative_anomaly <- 
      SCOTTSL3_negative_anomaly + CCI_SCOTTSL3$anomaly[i]
  } else {
    SCOTTSL3_negative_anomaly <- 0
  }
  SCOTTSL3_DHM[i] <- SCOTTSL3_negative_anomaly
}

CCI_SCOTTSL3 <- CCI_SCOTTSL3 %>% 
  add_column(SCOTTSL3_DHM)

#DHM calculations for NOAA dataset
SCOTTSL3_DHM <- rep(0,nrow(NOAA_SCOTTSL3))
SCOTTSL3_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTSL3)){
  if(NOAA_SCOTTSL3$anomaly[i] > 0) {
    SCOTTSL3_negative_anomaly <- 
      SCOTTSL3_negative_anomaly + NOAA_SCOTTSL3$anomaly[i]
  } else {
    SCOTTSL3_negative_anomaly <- 0
  }
  SCOTTSL3_DHM[i] <- SCOTTSL3_negative_anomaly
}

NOAA_SCOTTSL3 <- NOAA_SCOTTSL3 %>% 
  add_column(SCOTTSL3_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTSL3_Combined <- rbind(CCI_SCOTTSL3, NOAA_SCOTTSL3)

#DHM in descending order
Max_DHM_CCI_SCOTTSL3 <- CCI_SCOTTSL3 %>% 
  arrange(desc(SCOTTSL3_DHM)) %>% 
  select(date, SCOTTSL3_DHM)
Max_DHM_NOAA_SCOTTSL3 <- NOAA_SCOTTSL3 %>% 
  arrange(desc(SCOTTSL3_DHM)) %>% 
  select(date, SCOTTSL3_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTSL3, Max_DHM_NOAA_SCOTTSL3), caption = "Degree Heating Month values in SCOTTSL3 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTSL3_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTSL3_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTSL3 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


 
```

\newpage
# **SCOTTSS1** Degree Heating Months Time Series

```{r DHM_SCOTTSS1, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
SCOTTSS1_DHM <- rep(0,nrow(CCI_SCOTTSS1))
SCOTTSS1_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTSS1)){
  if(CCI_SCOTTSS1$anomaly[i] > 0) {
    SCOTTSS1_negative_anomaly <- 
      SCOTTSS1_negative_anomaly + CCI_SCOTTSS1$anomaly[i]
  } else {
    SCOTTSS1_negative_anomaly <- 0
  }
  SCOTTSS1_DHM[i] <- SCOTTSS1_negative_anomaly
}

CCI_SCOTTSS1 <- CCI_SCOTTSS1 %>% 
  add_column(SCOTTSS1_DHM)

#DHM calculations for NOAA dataset
SCOTTSS1_DHM <- rep(0,nrow(NOAA_SCOTTSS1))
SCOTTSS1_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTSS1)){
  if(NOAA_SCOTTSS1$anomaly[i] > 0) {
    SCOTTSS1_negative_anomaly <- 
      SCOTTSS1_negative_anomaly + NOAA_SCOTTSS1$anomaly[i]
  } else {
    SCOTTSS1_negative_anomaly <- 0
  }
  SCOTTSS1_DHM[i] <- SCOTTSS1_negative_anomaly
}

NOAA_SCOTTSS1 <- NOAA_SCOTTSS1 %>% 
  add_column(SCOTTSS1_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTSS1_Combined <- rbind(CCI_SCOTTSS1, NOAA_SCOTTSS1)

#DHM in descending order
Max_DHM_CCI_SCOTTSS1 <- CCI_SCOTTSS1 %>% 
  arrange(desc(SCOTTSS1_DHM)) %>% 
  select(date, SCOTTSS1_DHM)
Max_DHM_NOAA_SCOTTSS1 <- NOAA_SCOTTSS1 %>% 
  arrange(desc(SCOTTSS1_DHM)) %>% 
  select(date, SCOTTSS1_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTSS1, Max_DHM_NOAA_SCOTTSS1), caption = "Degree Heating Month values in SCOTTSS1 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTSS1_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTSS1_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTSS1 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


 
```

\newpage
# **SCOTTSS2** Degree Heating Months Time Series

```{r DHM_SCOTTSS2, echo = FALSE, message = FALSE}



#DHM calculations for CCI dataset 
SCOTTSS2_DHM <- rep(0,nrow(CCI_SCOTTSS2))
SCOTTSS2_negative_anomaly <- 0
for (i in 1:nrow(CCI_SCOTTSS2)){
  if(CCI_SCOTTSS2$anomaly[i] > 0) {
    SCOTTSS2_negative_anomaly <- 
      SCOTTSS2_negative_anomaly + CCI_SCOTTSS2$anomaly[i]
  } else {
    SCOTTSS2_negative_anomaly <- 0
  }
  SCOTTSS2_DHM[i] <- SCOTTSS2_negative_anomaly
}

CCI_SCOTTSS2 <- CCI_SCOTTSS2 %>% 
  add_column(SCOTTSS2_DHM)

#DHM calculations for NOAA dataset
SCOTTSS2_DHM <- rep(0,nrow(NOAA_SCOTTSS2))
SCOTTSS2_negative_anomaly <- 0
for (i in 1:nrow(NOAA_SCOTTSS2)){
  if(NOAA_SCOTTSS2$anomaly[i] > 0) {
    SCOTTSS2_negative_anomaly <- 
      SCOTTSS2_negative_anomaly + NOAA_SCOTTSS2$anomaly[i]
  } else {
    SCOTTSS2_negative_anomaly <- 0
  }
  SCOTTSS2_DHM[i] <- SCOTTSS2_negative_anomaly
}

NOAA_SCOTTSS2 <- NOAA_SCOTTSS2 %>% 
  add_column(SCOTTSS2_DHM)

#DHM calculations for Coral Core dataset
#no coral core at this site

#Combining datasets with DHM calculations
SCOTTSS2_Combined <- rbind(CCI_SCOTTSS2, NOAA_SCOTTSS2)

#DHM in descending order
Max_DHM_CCI_SCOTTSS2 <- CCI_SCOTTSS2 %>% 
  arrange(desc(SCOTTSS2_DHM)) %>% 
  select(date, SCOTTSS2_DHM)
Max_DHM_NOAA_SCOTTSS2 <- NOAA_SCOTTSS2 %>% 
  arrange(desc(SCOTTSS2_DHM)) %>% 
  select(date, SCOTTSS2_DHM)


knitr::kable(list(Max_DHM_CCI_SCOTTSS2, Max_DHM_NOAA_SCOTTSS2), caption = "Degree Heating Month values in SCOTTSS2 from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
SCOTTSS2_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = SCOTTSS2_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "SCOTTSS2 Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```

\newpage
# **BUN05A** Degree Heating Months Time Series
```{r DHM_BUN05A, echo = FALSE, message = FALSE}

#DHM calculations for CCI dataset 
BUN05A_DHM <- rep(0,nrow(CCI_BUN05A))
BUN05A_negative_anomaly <- 0
for (i in 1:nrow(CCI_BUN05A)){
  if(CCI_BUN05A$anomaly[i] > 0) {
    BUN05A_negative_anomaly <- 
      BUN05A_negative_anomaly + CCI_BUN05A$anomaly[i]
  } else {
    BUN05A_negative_anomaly <- 0
  }
  BUN05A_DHM[i] <- BUN05A_negative_anomaly
}

CCI_BUN05A <- CCI_BUN05A %>% 
  add_column(BUN05A_DHM)

#DHM calculations for NOAA dataset
BUN05A_DHM <- rep(0,nrow(NOAA_BUN05A))
BUN05A_negative_anomaly <- 0
for (i in 1:nrow(NOAA_BUN05A)){
  if(NOAA_BUN05A$anomaly[i] > 0) {
    BUN05A_negative_anomaly <- 
      BUN05A_negative_anomaly + NOAA_BUN05A$anomaly[i]
  } else {
    BUN05A_negative_anomaly <- 0
  }
  BUN05A_DHM[i] <- BUN05A_negative_anomaly
}

NOAA_BUN05A <- NOAA_BUN05A %>% 
  add_column(BUN05A_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
BUN05A_Combined <- rbind(CCI_BUN05A, NOAA_BUN05A)

#DHM in descending order
Max_DHM_CCI_BUN05A <- CCI_BUN05A %>% 
  arrange(desc(BUN05A_DHM)) %>% 
  select(date, BUN05A_DHM)
Max_DHM_NOAA_BUN05A <- NOAA_BUN05A %>% 
  arrange(desc(BUN05A_DHM)) %>% 
  select(date, BUN05A_DHM)


knitr::kable(list(Max_DHM_CCI_BUN05A, Max_DHM_NOAA_BUN05A), caption = "Degree Heating Month values in BUN05A from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
BUN05A_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = BUN05A_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "BUN05A Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )
```

\newpage
# **Bundegi** Degree Heating Months Time Series

```{r DHM_Bundegi, echo = FALSE, message = FALSE}

#DHM calculations for CCI dataset 
Bundegi_DHM <- rep(0,nrow(CCI_Bundegi))
Bundegi_negative_anomaly <- 0
for (i in 1:nrow(CCI_Bundegi)){
  if(CCI_Bundegi$anomaly[i] > 0) {
    Bundegi_negative_anomaly <- 
      Bundegi_negative_anomaly + CCI_Bundegi$anomaly[i]
  } else {
    Bundegi_negative_anomaly <- 0
  }
  Bundegi_DHM[i] <- Bundegi_negative_anomaly
}

CCI_Bundegi <- CCI_Bundegi %>% 
  add_column(Bundegi_DHM)

#DHM calculations for NOAA dataset
Bundegi_DHM <- rep(0,nrow(NOAA_Bundegi))
Bundegi_negative_anomaly <- 0
for (i in 1:nrow(NOAA_Bundegi)){
  if(NOAA_Bundegi$anomaly[i] > 0) {
    Bundegi_negative_anomaly <- 
      Bundegi_negative_anomaly + NOAA_Bundegi$anomaly[i]
  } else {
    Bundegi_negative_anomaly <- 0
  }
  Bundegi_DHM[i] <- Bundegi_negative_anomaly
}

NOAA_Bundegi <- NOAA_Bundegi %>% 
  add_column(Bundegi_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
Bundegi_Combined <- rbind(CCI_Bundegi, NOAA_Bundegi)

#DHM in descending order
Max_DHM_CCI_Bundegi <- CCI_Bundegi %>% 
  arrange(desc(Bundegi_DHM)) %>% 
  select(date, Bundegi_DHM)
Max_DHM_NOAA_Bundegi <- NOAA_Bundegi %>% 
  arrange(desc(Bundegi_DHM)) %>% 
  select(date, Bundegi_DHM)


knitr::kable(list(Max_DHM_CCI_Bundegi, Max_DHM_NOAA_Bundegi), caption = "Degree Heating Month values in 08BND and 13BND from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
Bundegi_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = Bundegi_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "08BND and 13BND Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )
```



\newpage
# **Tantabiddi 08TNT** Degree Heating Months Time Series

```{r DHM_Tantabiddi_08TNT, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
Tantabiddi_DHM <- rep(0,nrow(CCI_Tantabiddi_08TNT))
Tantabiddi_negative_anomaly <- 0
for (i in 1:nrow(CCI_Tantabiddi_08TNT)){
  if(CCI_Tantabiddi_08TNT$anomaly[i] > 0) {
    Tantabiddi_negative_anomaly <- 
      Tantabiddi_negative_anomaly + CCI_Tantabiddi_08TNT$anomaly[i]
  } else {
    Tantabiddi_negative_anomaly <- 0
  }
  Tantabiddi_DHM[i] <- Tantabiddi_negative_anomaly
}

CCI_Tantabiddi_08TNT <- CCI_Tantabiddi_08TNT %>%
  add_column(Tantabiddi_DHM) %>% 
  rename(`08TNT_DHM` = Tantabiddi_DHM)

#DHM calculations for NOAA dataset
Tantabiddi_DHM <- rep(0,nrow(NOAA_Tantabiddi_08TNT))
Tantabiddi_negative_anomaly <- 0
for (i in 1:nrow(NOAA_Tantabiddi_08TNT)){
  if(NOAA_Tantabiddi_08TNT$anomaly[i] > 0) {
    Tantabiddi_negative_anomaly <- 
      Tantabiddi_negative_anomaly + NOAA_Tantabiddi_08TNT$anomaly[i]
  } else {
    Tantabiddi_negative_anomaly <- 0
  }
  Tantabiddi_DHM[i] <- Tantabiddi_negative_anomaly
}

NOAA_Tantabiddi_08TNT <- NOAA_Tantabiddi_08TNT %>% 
  add_column(Tantabiddi_DHM) %>% 
  rename(`08TNT_DHM` = Tantabiddi_DHM)

#DHM calculations for Coral Core (CCI) dataset
`08TNT_DHM` <- rep(0,nrow(CCore_08TNT_CCI))
`08TNT_negative_anomaly` <- 0
for (i in 1:nrow(CCore_08TNT_CCI)){
  if(CCore_08TNT_CCI$anomaly[i] > 0) {
    `08TNT_negative_anomaly` <- 
      `08TNT_negative_anomaly` + CCore_08TNT_CCI$anomaly[i]
  } else {
    `08TNT_negative_anomaly` <- 0
  }
  `08TNT_DHM`[i] <- `08TNT_negative_anomaly`
}

CCore_08TNT_CCI <- CCore_08TNT_CCI %>% 
  add_column(`08TNT_DHM`)

#DHM calculations for Coral Core (NOAA) dataset
`08TNT_DHM` <- rep(0,nrow(CCore_08TNT_NOAA))
`08TNT_negative_anomaly` <- 0
for (i in 1:nrow(CCore_08TNT_NOAA)){
  if(CCore_08TNT_NOAA$anomaly[i] > 0) {
   ` 08TNT_negative_anomaly` <- 
      `08TNT_negative_anomaly` + CCore_08TNT_NOAA$anomaly[i]
  } else {
    `08TNT_negative_anomaly` <- 0
  }
 `08TNT_DHM`[i] <- `08TNT_negative_anomaly`
}

CCore_08TNT_NOAA <- CCore_08TNT_NOAA %>% 
  add_column(`08TNT_DHM`)

#Combining datasets with DHM calculations
Tantabiddi_08TNT_Combined <- rbind(CCI_Tantabiddi_08TNT, NOAA_Tantabiddi_08TNT, CCore_08TNT_CCI, CCore_08TNT_NOAA)

#DHM >= 1
High_08TNT_DHM <- Tantabiddi_08TNT_Combined %>% 
  filter(`08TNT_DHM` >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, `08TNT_DHM`) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = `08TNT_DHM`) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_08TNT_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in 08TNT" = 3), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1996 to 2008")

#Visualising DHM values in CCI, NOAA and CCore 
Tantabiddi_08TNT_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = `08TNT_DHM`, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "08TNT Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


 
```

\newpage
# **Tantabiddi 13TNT** Degree Heating Months Time Series
```{r DHM_Tantabiddi_13TNT, echo = FALSE, message = FALSE}

#DHM calculations for CCI dataset 
Tantabiddi_DHM <- rep(0,nrow(CCI_Tantabiddi_13TNT))
Tantabiddi_negative_anomaly <- 0
for (i in 1:nrow(CCI_Tantabiddi_13TNT)){
  if(CCI_Tantabiddi_13TNT$anomaly[i] > 0) {
    Tantabiddi_negative_anomaly <- 
      Tantabiddi_negative_anomaly + CCI_Tantabiddi_13TNT$anomaly[i]
  } else {
    Tantabiddi_negative_anomaly <- 0
  }
  Tantabiddi_DHM[i] <- Tantabiddi_negative_anomaly
}

CCI_Tantabiddi_13TNT <- CCI_Tantabiddi_13TNT %>%
  add_column(Tantabiddi_DHM) %>% 
  rename(`13TNT_DHM` = Tantabiddi_DHM)

#DHM calculations for NOAA dataset
Tantabiddi_DHM <- rep(0,nrow(NOAA_Tantabiddi_13TNT))
Tantabiddi_negative_anomaly <- 0
for (i in 1:nrow(NOAA_Tantabiddi_13TNT)){
  if(NOAA_Tantabiddi_13TNT$anomaly[i] > 0) {
    Tantabiddi_negative_anomaly <- 
      Tantabiddi_negative_anomaly + NOAA_Tantabiddi_13TNT$anomaly[i]
  } else {
    Tantabiddi_negative_anomaly <- 0
  }
  Tantabiddi_DHM[i] <- Tantabiddi_negative_anomaly
}

NOAA_Tantabiddi_13TNT <- NOAA_Tantabiddi_13TNT %>% 
  add_column(Tantabiddi_DHM) %>% 
  rename(`13TNT_DHM` = Tantabiddi_DHM)

#DHM calculations for Coral Core (CCI) dataset
`13TNT_DHM` <- rep(0,nrow(CCore_13TNT_CCI))
`13TNT_negative_anomaly` <- 0
for (i in 1:nrow(CCore_13TNT_CCI)){
  if(CCore_13TNT_CCI$anomaly[i] > 0) {
    `13TNT_negative_anomaly` <- 
      `13TNT_negative_anomaly` + CCore_13TNT_CCI$anomaly[i]
  } else {
    `13TNT_negative_anomaly` <- 0
  }
  `13TNT_DHM`[i] <- `13TNT_negative_anomaly`
}

CCore_13TNT_CCI <- CCore_13TNT_CCI %>% 
  add_column(`13TNT_DHM`)

#DHM calculations for Coral Core (NOAA) dataset
`13TNT_DHM` <- rep(0,nrow(CCore_13TNT_NOAA))
`13TNT_negative_anomaly` <- 0
for (i in 1:nrow(CCore_13TNT_NOAA)){
  if(CCore_13TNT_NOAA$anomaly[i] > 0) {
   ` 13TNT_negative_anomaly` <- 
      `13TNT_negative_anomaly` + CCore_13TNT_NOAA$anomaly[i]
  } else {
    `13TNT_negative_anomaly` <- 0
  }
 `13TNT_DHM`[i] <- `13TNT_negative_anomaly`
}

CCore_13TNT_NOAA <- CCore_13TNT_NOAA %>% 
  add_column(`13TNT_DHM`)

#Combining datasets with DHM calculations
Tantabiddi_13TNT_Combined <- rbind(CCI_Tantabiddi_13TNT, NOAA_Tantabiddi_13TNT, CCore_13TNT_CCI, CCore_13TNT_NOAA)

#DHM >= 1
High_13TNT_DHM <- Tantabiddi_13TNT_Combined %>% 
  filter(`13TNT_DHM` >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, `13TNT_DHM`) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = `13TNT_DHM`) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_13TNT_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in 13TNT" = 4), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 2004 to 2013")

#Visualising DHM values in CCI, NOAA and CCore 
Tantabiddi_13TNT_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = `13TNT_DHM`, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "13TNT Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )

```


\newpage
# **TNT** Degree Heating Months Time Series

```{r DHM_TNT, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
TNT_DHM <- rep(0,nrow(CCI_TNT))
TNT_negative_anomaly <- 0
for (i in 1:nrow(CCI_TNT)){
  if(CCI_TNT$anomaly[i] > 0) {
    TNT_negative_anomaly <- 
      TNT_negative_anomaly + CCI_TNT$anomaly[i]
  } else {
    TNT_negative_anomaly <- 0
  }
  TNT_DHM[i] <- TNT_negative_anomaly
}

CCI_TNT <- CCI_TNT %>% 
  add_column(TNT_DHM)

#DHM calculations for NOAA dataset
TNT_DHM <- rep(0,nrow(NOAA_TNT))
TNT_negative_anomaly <- 0
for (i in 1:nrow(NOAA_TNT)){
  if(NOAA_TNT$anomaly[i] > 0) {
    TNT_negative_anomaly <- 
      TNT_negative_anomaly + NOAA_TNT$anomaly[i]
  } else {
    TNT_negative_anomaly <- 0
  }
  TNT_DHM[i] <- TNT_negative_anomaly
}

NOAA_TNT <- NOAA_TNT %>% 
  add_column(TNT_DHM)

#DHM calculations for Coral Core (CCI) dataset
TNT_DHM <- rep(0,nrow(CCore_TNT_CCI))
TNT_negative_anomaly <- 0
for (i in 1:nrow(CCore_TNT_CCI)){
  if(CCore_TNT_CCI$anomaly[i] > 0) {
    TNT_negative_anomaly <- 
      TNT_negative_anomaly + CCore_TNT_CCI$anomaly[i]
  } else {
    TNT_negative_anomaly <- 0
  }
  TNT_DHM[i] <- TNT_negative_anomaly
}

CCore_TNT_CCI <- CCore_TNT_CCI %>% 
  add_column(TNT_DHM)

#DHM calculations for Coral Core (NOAA) dataset
TNT_DHM <- rep(0,nrow(CCore_TNT_NOAA))
TNT_negative_anomaly <- 0
for (i in 1:nrow(CCore_TNT_NOAA)){
  if(CCore_TNT_NOAA$anomaly[i] > 0) {
    TNT_negative_anomaly <- 
      TNT_negative_anomaly + CCore_TNT_NOAA$anomaly[i]
  } else {
    TNT_negative_anomaly <- 0
  }
  TNT_DHM[i] <- TNT_negative_anomaly
}

CCore_TNT_NOAA <- CCore_TNT_NOAA %>% 
  add_column(TNT_DHM)

#Combining datasets with DHM calculations
TNT_Combined <- rbind(CCI_TNT, NOAA_TNT, CCore_TNT_CCI, CCore_TNT_NOAA)

#DHM >= 1
High_TNT_DHM <- TNT_Combined %>% 
  filter(TNT_DHM >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, TNT_DHM) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = TNT_DHM) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_TNT_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in TNT" = 3), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1985 to 1994")

#Visualising DHM values in CCI, NOAA and CCore 
TNT_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = TNT_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "TNT Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source") +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )


 
```

\newpage
# **TNT07C** Degree Heating Months Time Series

```{r DHM_TNT07C, echo = FALSE, message = FALSE}



#DHM calculations for CCI dataset 
TNT07C_DHM <- rep(0,nrow(CCI_TNT07C))
TNT07C_negative_anomaly <- 0
for (i in 1:nrow(CCI_TNT07C)){
  if(CCI_TNT07C$anomaly[i] > 0) {
    TNT07C_negative_anomaly <- 
      TNT07C_negative_anomaly + CCI_TNT07C$anomaly[i]
  } else {
    TNT07C_negative_anomaly <- 0
  }
  TNT07C_DHM[i] <- TNT07C_negative_anomaly
}

CCI_TNT07C <- CCI_TNT07C %>% 
  add_column(TNT07C_DHM)

#DHM calculations for NOAA dataset
TNT07C_DHM <- rep(0,nrow(NOAA_TNT07C))
TNT07C_negative_anomaly <- 0
for (i in 1:nrow(NOAA_TNT07C)){
  if(NOAA_TNT07C$anomaly[i] > 0) {
    TNT07C_negative_anomaly <- 
      TNT07C_negative_anomaly + NOAA_TNT07C$anomaly[i]
  } else {
    TNT07C_negative_anomaly <- 0
  }
  TNT07C_DHM[i] <- TNT07C_negative_anomaly
}

NOAA_TNT07C <- NOAA_TNT07C %>% 
  add_column(TNT07C_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
TNT07C_Combined <- rbind(CCI_TNT07C, NOAA_TNT07C)

#DHM in descending order
Max_DHM_CCI_TNT07C <- CCI_TNT07C %>% 
  arrange(desc(TNT07C_DHM)) %>% 
  select(date, TNT07C_DHM)
Max_DHM_NOAA_TNT07C <- NOAA_TNT07C %>% 
  arrange(desc(TNT07C_DHM)) %>% 
  select(date, TNT07C_DHM)


knitr::kable(list(Max_DHM_CCI_TNT07C, Max_DHM_NOAA_TNT07C), caption = "Degree Heating Month values in TNT07C from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
TNT07C_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = TNT07C_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "TNT07C Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```


\newpage
# **Wallabi Island** Degree Heating Months Time Series

```{r DHM_Wallabi_Island, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
Wallabi_Island_DHM <- rep(0,nrow(CCI_Wallabi_Island))
Wallabi_Island_negative_anomaly <- 0
for (i in 1:nrow(CCI_Wallabi_Island)){
  if(CCI_Wallabi_Island$anomaly[i] > 0) {
    Wallabi_Island_negative_anomaly <- 
      Wallabi_Island_negative_anomaly + CCI_Wallabi_Island$anomaly[i]
  } else {
    Wallabi_Island_negative_anomaly <- 0
  }
  Wallabi_Island_DHM[i] <- Wallabi_Island_negative_anomaly
}

CCI_Wallabi_Island <- CCI_Wallabi_Island %>% 
  add_column(Wallabi_Island_DHM)

#DHM calculations for NOAA dataset
Wallabi_Island_DHM <- rep(0,nrow(NOAA_Wallabi_Island))
Wallabi_Island_negative_anomaly <- 0
for (i in 1:nrow(NOAA_Wallabi_Island)){
  if(NOAA_Wallabi_Island$anomaly[i] > 0) {
    Wallabi_Island_negative_anomaly <- 
      Wallabi_Island_negative_anomaly + NOAA_Wallabi_Island$anomaly[i]
  } else {
    Wallabi_Island_negative_anomaly <- 0
  }
  Wallabi_Island_DHM[i] <- Wallabi_Island_negative_anomaly
}

NOAA_Wallabi_Island <- NOAA_Wallabi_Island %>% 
  add_column(Wallabi_Island_DHM)

#DHM calculations for Coral Core (CCI) dataset
Wallabi_Island_DHM <- rep(0,nrow(CCore_Wallabi_Island_CCI))
Wallabi_Island_negative_anomaly <- 0
for (i in 1:nrow(CCore_Wallabi_Island_CCI)){
  if(CCore_Wallabi_Island_CCI$anomaly[i] > 0) {
    Wallabi_Island_negative_anomaly <- 
      Wallabi_Island_negative_anomaly + CCore_Wallabi_Island_CCI$anomaly[i]
  } else {
    Wallabi_Island_negative_anomaly <- 0
  }
  Wallabi_Island_DHM[i] <- Wallabi_Island_negative_anomaly
}

CCore_Wallabi_Island_CCI <- CCore_Wallabi_Island_CCI %>% 
  add_column(Wallabi_Island_DHM)

#DHM calculations for Coral Core (NOAA) dataset
Wallabi_Island_DHM <- rep(0,nrow(CCore_Wallabi_Island_NOAA))
Wallabi_Island_negative_anomaly <- 0
for (i in 1:nrow(CCore_Wallabi_Island_NOAA)){
  if(CCore_Wallabi_Island_NOAA$anomaly[i] > 0) {
    Wallabi_Island_negative_anomaly <- 
      Wallabi_Island_negative_anomaly + CCore_Wallabi_Island_NOAA$anomaly[i]
  } else {
    Wallabi_Island_negative_anomaly <- 0
  }
  Wallabi_Island_DHM[i] <- Wallabi_Island_negative_anomaly
}

CCore_Wallabi_Island_NOAA <- CCore_Wallabi_Island_NOAA %>% 
  add_column(Wallabi_Island_DHM)

#Combining datasets with DHM calculations
Wallabi_Island_Combined <- rbind(CCI_Wallabi_Island, NOAA_Wallabi_Island, CCore_Wallabi_Island_CCI, CCore_Wallabi_Island_NOAA)

#DHM >= 1
High_Wallabi_Island_DHM <- Wallabi_Island_Combined %>% 
  filter(Wallabi_Island_DHM >= 1) %>% 
  select(monthly_date, Reef_Site, Data_Type, Wallabi_Island_DHM) %>% 
  mutate(monthly_date = yearmonth(monthly_date)) %>% 
  pivot_wider(names_from = Data_Type, values_from = Wallabi_Island_DHM) %>% 
  arrange(-desc(monthly_date)) %>% 
  rename(Date = monthly_date, Site = Reef_Site)

kbl(High_Wallabi_Island_DHM) %>% 
  kable_styling(position = "center") %>% 
  add_header_above(c("Degree Heating Month Values in Wallabi Island" = 4), bold = TRUE) %>% 
  add_footnote("Coral Core Date Range is from 1985 to 1994")

#Visualising DHM values in CCI, NOAA and CCore 
Wallabi_Island_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = Wallabi_Island_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "Wallabi Island Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )



```


\newpage
# **HAB05B** Degree Heating Months Time Series

```{r DHM_HAB05B, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
HAB05B_DHM <- rep(0,nrow(CCI_HAB05B))
HAB05B_negative_anomaly <- 0
for (i in 1:nrow(CCI_HAB05B)){
  if(CCI_HAB05B$anomaly[i] > 0) {
    HAB05B_negative_anomaly <- 
      HAB05B_negative_anomaly + CCI_HAB05B$anomaly[i]
  } else {
    HAB05B_negative_anomaly <- 0
  }
  HAB05B_DHM[i] <- HAB05B_negative_anomaly
}

CCI_HAB05B <- CCI_HAB05B %>% 
  add_column(HAB05B_DHM)

#DHM calculations for NOAA dataset
HAB05B_DHM <- rep(0,nrow(NOAA_HAB05B))
HAB05B_negative_anomaly <- 0
for (i in 1:nrow(NOAA_HAB05B)){
  if(NOAA_HAB05B$anomaly[i] > 0) {
    HAB05B_negative_anomaly <- 
      HAB05B_negative_anomaly + NOAA_HAB05B$anomaly[i]
  } else {
    HAB05B_negative_anomaly <- 0
  }
  HAB05B_DHM[i] <- HAB05B_negative_anomaly
}

NOAA_HAB05B <- NOAA_HAB05B %>% 
  add_column(HAB05B_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
HAB05B_Combined <- rbind(CCI_HAB05B, NOAA_HAB05B)

#DHM in descending order
Max_DHM_CCI_HAB05B <- CCI_HAB05B %>% 
  arrange(desc(HAB05B_DHM)) %>% 
  select(date, HAB05B_DHM)
Max_DHM_NOAA_HAB05B <- NOAA_HAB05B %>% 
  arrange(desc(HAB05B_DHM)) %>% 
  select(date, HAB05B_DHM)


knitr::kable(list(Max_DHM_CCI_HAB05B, Max_DHM_NOAA_HAB05B), caption = "Degree Heating Month values in HAB05B from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
HAB05B_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = HAB05B_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "HAB05B Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  ) 


 
```


\newpage
# **HAB10A** Degree Heating Months Time Series

```{r DHM_HAB10A, echo = FALSE, message = FALSE}


#DHM calculations for CCI dataset 
HAB10A_DHM <- rep(0,nrow(CCI_HAB10A))
HAB10A_negative_anomaly <- 0
for (i in 1:nrow(CCI_HAB10A)){
  if(CCI_HAB10A$anomaly[i] > 0) {
    HAB10A_negative_anomaly <- 
      HAB10A_negative_anomaly + CCI_HAB10A$anomaly[i]
  } else {
    HAB10A_negative_anomaly <- 0
  }
  HAB10A_DHM[i] <- HAB10A_negative_anomaly
}

CCI_HAB10A <- CCI_HAB10A %>% 
  add_column(HAB10A_DHM)

#DHM calculations for NOAA dataset
HAB10A_DHM <- rep(0,nrow(NOAA_HAB10A))
HAB10A_negative_anomaly <- 0
for (i in 1:nrow(NOAA_HAB10A)){
  if(NOAA_HAB10A$anomaly[i] > 0) {
    HAB10A_negative_anomaly <- 
      HAB10A_negative_anomaly + NOAA_HAB10A$anomaly[i]
  } else {
    HAB10A_negative_anomaly <- 0
  }
  HAB10A_DHM[i] <- HAB10A_negative_anomaly
}

NOAA_HAB10A <- NOAA_HAB10A %>% 
  add_column(HAB10A_DHM)

#DHM calculations for Coral Core dataset
#pending

#Combining datasets with DHM calculations
HAB10A_Combined <- rbind(CCI_HAB10A, NOAA_HAB10A)

#DHM in descending order
Max_DHM_CCI_HAB10A <- CCI_HAB10A %>% 
  arrange(desc(HAB10A_DHM)) %>% 
  select(date, HAB10A_DHM)
Max_DHM_NOAA_HAB10A <- NOAA_HAB10A %>% 
  arrange(desc(HAB10A_DHM)) %>% 
  select(date, HAB10A_DHM)


knitr::kable(list(Max_DHM_CCI_HAB10A, Max_DHM_NOAA_HAB10A), caption = "Degree Heating Month values in HAB10A from CCI (left) and NOAA (right)", col.names = c("Date", "DHM value"))

#Visualising DHM values in CCI, NOAA and CCore 
HAB10A_Combined %>% 
  ggplot()+
  geom_line(aes(x = monthly_date, y = HAB10A_DHM, color = Data_Type), alpha = 0.3, size = 2) +
  labs(x = "Date", y = "Degree Heating Months", title = "HAB10A Degree Heating Month values time plot")+
  scale_color_discrete_qualitative(name = "Data Source")  +
  scale_y_continuous(breaks = c(0, 2, 4)) +
  theme(panel.grid.major.y = element_line(color = "grey", linetype = "dashed"),
        legend.key = element_rect(fill = "transparent"),
        plot.title = element_text( face = "bold")
  )  


 
```

